Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-14 shanghai.tex
Summary of sections

% !TEX encoding = UTF-8 Unicode
\documentclass[11pt]{amsart}
\title[Geometrization of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
\usepackage[british]{babel}
\usepackage{datetime}
\date{\today}
\author{Clifton Cunningham}
\address{University of Calgary}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
\email{roed.math@gmail.com}
\usepackage[utf8]{inputenc}
\renewcommand{\baselinestretch}{1.2}
\usepackage[notcite]{showkeys}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[shortalphabetic]{amsrefs}
\usepackage[alphabetic]{amsrefs}
\renewcommand\MR{\relax}
\usepackage{xypic}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{yfonts}
\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
\usepackage{manfnt}
%\usepackage{makeidx}

@@

\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\W}{W}
\newcommand{\Frob}[1]{{\operatorname{F}_{#1}}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\Pic}{Pic}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\Nm}{Nm}
\DeclareMathOperator{\trace}{Tr}

@@

%\input{introduction}
%In his celebrated thesis, John Tate writes 
%\begin{quotation}
%    {\it Concerning the characters of $k^*$ [the
%    multiplicative group of a $\mathfrak{p}$-adic field], the
%    situation is different from that of $k^+$.  First of all, we are
%    interested in continuous multiplicative maps $\alpha \mapsto
%    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
%    bounded ones, and shall call such a map a quasi-character,
%    reserving the word ``character'' for the conventional character of
%    absolute value $1$. Secondly, we shall find no model for the group
%    of quasi-characters, or even for the group of characters, though
%    such a model would be of the utmost importance.}
%  \cite{Tate:thesis}*{\S 2.3}
%\end{quotation}
%\noindent
What is a quasicharacter sheaf?
Let $G$ be a smooth commutative group scheme locally of finite
type over a finite field $\Fq$; $G$ need not be reductive, connected, or of
finite type over $\Fq$. Fix a prime $\ell$ that does not divide
$q$, write $m : \GxG \to G$ for the multiplication morphism,
$\bG$ for the base change of $G$ to $\bFq$ and
$\Frob{G} : \bG \to \bG$ for the Frobenius automorphism.
A quasicharacter sheaf on $G$ is a triple $\cs{L}\ceq
(\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a rank-$1$ local system on $\bG$ and $\mu: m^*
\gcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gcs{L} \to \gcs{L}$ are isomorphisms;
$\mu$ and $\phi$ are required to satisfy natural conditions explained below.

In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves.
Since it is a rigid symmetric monoidal category,
and the set of isomorphism classes $\QCiso{G}$ forms a group.
Motivated by the sheaf-function dictionary for commutative, connected
algebraic groups \cite{SGA4.5}, we explore the trace of Frobenius morphism
\[
\QCiso{G} \to \Hom(G(\Fq), \EEx)
\]
and show that it is an isomorphism in Theorem \ref{thm:snake}, assuming only
that the component group of $G$ is finitely generated.

We apply Theorem \ref{thm:snake} to the geometrization of quasicharacters
of non-Archimedian tori in part 2.  Let $K$ be a non-Archimedian local field
with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
Write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$.
Let $T$ be a maximal torus defined over $K$.  The N\'eron model $\TT$ of $T$
is a smooth group scheme over $\OK$ with generic fiber $T$ and a canonical isomorphism
$\TT(\OK) \cong T(K)$.  For each positive integer $d$, let $\GN{T}_d$ be the
Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^d}$; the commutative
group scheme $\GN{T}_d$ plays the r\^{o}le of $G$, above.  Theorem \ref{thm:application}
now provides a geometrization of quasicharacters of $T$ in the form of a canonical isomorphism
\[
\QCiso{\GN{T}_d} 
\iso
\Hom_{< d}(T(K),\EEx)
\] 
between quasicharacters on $\GN{T}_d$ and characters of $T(K)$ with depth less than $d$.

@@

We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
Analogous sheaves on connected, commutative algebraic groups were first studied
by Deligne \cite{SGA4.5}, and more recently Drinfeld has referred to such objects
as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem \ref{thm:snake}
is a direct generalization of the sheaf-function dictionary to the case of commutative
group schemes which are not necessarily connected or finite type.  The other main use
of the term ``character sheaf'' traces back to Lusztig \cite{}.  Most of his energy is devoted to
handling non-commutative groups and though he does define character sheaves for some
non-connected groups, he restricts his attention to reductive groups with cyclic component group.
For extensions of $\ZZ/n\ZZ$ by a torus, it is not difficult to relate his Frobenius-stable character
sheaves to our quasicharacter sheaves.

We close the introduction with a more detailed description of the structure of this paper.
In Section \ref{sec:category} we define quasicharacter sheaves and give an interpretation of
them as a Weil sheaf with a Galois action.

@@

\Clifton{Declare definitions - about 10 of them.}

\part{Smooth commutative group schemes lft over finite fields}

@@

\Clifton{Now that I'm working on the functoriality of trace of Frobenius, I  think the source of the functoriality is mainly this: $\QC$ is a stack. I'm thinking about this now.}

@@

\section{Pull-back and products}\label{subsection:pullback}

@@

In the opposite direction, let $\Nm_{k'/k} : G(k') \to G(k)$ be the norm map and consider the group homomorhism:
\Clifton{How is $\Nm$ defined?}
\[
\Nm_{k'/k}^* : G(k)^* \to G(k')^* \qquad \text{defined by}\qquad \chi \mapsto \chi\circ \Nm_{k'/k}.
\]
We can also interpret this operation on characters in terms of quasicharacter sheaves, as follows.

@@

\section{Connected commutative algebraic groups}

@@

  Let $(\cs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
  Recall the definition of the character $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
  Let $f : G\to G$ be the Lang isogeny.
  Recall that $\ker f = G(\Fq) = G^\Frob{\Fq}$; 
  in particular, the action of $\Gal(\bFq/\Fq)$ on $\ker f$ is trivial.
  Let $V = \EE$ and let $\psi : \ker f \to \Aut(V)$ be the representation given by 
  $\psi(g)(v) = \trFrob{\cs{L}}(g) v$ for $v\in V$. 
  Then $(f,\psi)$ is a finite quasicharacter sheaf.

@@

\section{Commutative \'etale group schemes}

@@

  Starting from $\cs{L}$, we define a cocyle $\tau_{\cs{L}} \in Z^1(\Weil{\Fq},G(\bFq)^*)$ as follows.
  For $x \in G(\bFq)$, $\cs{L}$ determines an isomorphism $\phi_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
  of one-dimensional $\EE$-vector spaces; define $\tau_\cs{L}$ by
  \begin{equation}\label{t}
   \phi_{x}(s(\Frob{\Fq}(x))) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
  \end{equation}
  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\cs{L}(\Frob{\Fq})(x)$ is just $t_\cs{L}(x)$, so the restriction of
  $\tau_\cs{L}(\Frob{k})$ to $G(k)$ is just $t_\cs{L}$.
  In general, conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
  the scalar $\tau_\cs{L}(\Frob{k})(x)$ is non-zero.  Moreover, condition~\ref{cs.1} forces
  $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$
  for all $x,y \in G(\bFq)$.  Now define $\tau_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ recursively by
  \[
   \tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} \tau_\cs{L}(\Frob{\Fq}^{n-1}),
  \]
  where $\Frob{\Fq}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
  to pointwise multiplication of functions.

  Although we used a global section $s$ in the definition of
  $\tau_\cs{L}$, the class of $\tau_\cs{L}$ does not depend on this
  choice. To see why, let $s_1$ and $s_2$ be two global sections of
  $\cs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
  For each $x \in G(\bFq)$ there is a unique scalar
  $a(x) \in \EEx$ such that $s_2(x) = a(x) s_1(x)$. Then \eqref{section} and
  condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
  defined by $\tau_0(\Frob{\Fq}) = \,^\Frob{\Fq} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
  so $\tau_2$ and $\tau_1$ are cohomologous. Thus
  \begin{equation}\label{cohomologous}
    \obj \QC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
    \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
  \end{equation}
  is independent of the choice of global sections made above.

@@

\section{On the cohomology of the dual of an etale group scheme}
%\input{etale-2}
%Define $\rho \colon \Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))
% \rightarrow \Hom(G(\Fq), \EEx)$ by $\rho(\phi)(g) =
% \phi(\Frob)(g)$.

@@

\begin{proposition}\label{prop:X}
  Let $X$ be a finitely generated abelian group equipped with an
  action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on
  $X$.  Then
  \begin{align*}
%    \Hh^1(\Fq, \Hom(X, \EEx)) &\xrightarrow{\rho} \Hom(\Hh^0(\Fq, X), \EEx) \\
    \Hh^1(\Fq, X^*) &\xrightarrow{\rho} \Hh^0(\Fq, X)^* \\
    \rho([z])(x) &= z(\Frob{\Fq})(x)
  \end{align*}
  is an isomorphism of groups.
\end{proposition}
\begin{proof}
  We first prove that $\rho$ is surjective.  Suppose that
  $f \in \Hom(X^\Frob{\Fq}, \EEx).$ Since $\EEx$ is divisible
  as an abelian group it is injective as a $\ZZ$-module and thus
  $\Ext^1_{\ZZ}(X/X^\Frob{\Fq}, \EEx) = 0$.  Applying the functor
  $\Hom(\mbox{---}, \EEx)$ to
  \[
  \begin{tikzcd}
  0 \rar & X^\Frob{\Fq} \rar & X \rar & X/X^\Frob{\Fq} \rar & 0
  \end{tikzcd}
  \]
  and considering the associated long exact sequence gives the
  existence of an $\tilde{f} \in \Hom(X, \EEx)$ restricting to
  $f$.  Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EEx))$ by
  mapping $\Frob{\Fq}$ to $\tilde{f}$.  Then $\rho([z]) = f$.

@@

\section{Restriction to the identity component}

@@

We have already seen that the trace of Frobenius defines a canonical homomorphism $\QCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
In this section we show that this homomorphism is functorial, in the following sense.
\Clifton{Fold this section into the main result on characters of local tori?}

@@

\section{Application to quasicharacters of bounded depth}

@@

\section{The geometrization of quasicharacters}

@@

\section{The transfer principle}

>>>>

% !TEX encoding = UTF-8 Unicode
\documentclass[11pt]{amsart}
\title[Geometrization of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
\usepackage[british]{babel}
\usepackage{datetime}
\date{\today}
\author{Clifton Cunningham}
\address{University of Calgary}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
\email{roed.math@gmail.com}
\usepackage[utf8]{inputenc}
\renewcommand{\baselinestretch}{1.2}
%\usepackage[notcite]{showkeys}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[shortalphabetic]{amsrefs}
\usepackage[alphabetic]{amsrefs}
\renewcommand\MR{\relax}
\usepackage{xypic}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{yfonts}
\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
\usepackage{manfnt}
%\usepackage{makeidx}

@@

\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\W}{W}
\newcommand{\Frob}[1]{\operatorname{F}_{#1}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\Pic}{Pic}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\Nm}{Nm}
\DeclareMathOperator{\trace}{Tr}

@@

%\input{introduction}
%In his celebrated thesis, John Tate writes 
%\begin{quotation}
%    {\it Concerning the characters of $k^*$ [the
%    multiplicative group of a $\mathfrak{p}$-adic field], the
%    situation is different from that of $k^+$.  First of all, we are
%    interested in continuous multiplicative maps $\alpha \mapsto
%    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
%    bounded ones, and shall call such a map a quasi-character,
%    reserving the word ``character'' for the conventional character of
%    absolute value $1$. Secondly, we shall find no model for the group
%    of quasi-characters, or even for the group of characters, though
%    such a model would be of the utmost importance.}
%  \cite{Tate:thesis}*{\S 2.3}
%\end{quotation}
%\noindent
What is a quasicharacter sheaf?
Let $G$ be a smooth commutative group scheme locally of finite
type over a finite field $\Fq$; $G$ need not be reductive, connected, or of
finite type over $\Fq$. Fix a prime $\ell$ that does not divide
$q$, write $m : \GxG \to G$ for the multiplication morphism,
$\bG$ for the base change of $G$ to $\bFq$ and
$\Frob{G} : \bG \to \bG$ for the Frobenius automorphism.
A quasicharacter sheaf on $G$ is a triple $\cs{L}\ceq
(\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a rank-$1$ $\ell$-adic local system on $\bG$ and $\mu: m^*
\gcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gcs{L} \to \gcs{L}$ are isomorphisms;
$\mu$ and $\phi$ are required to satisfy natural conditions explained below.

In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves.
Since it is a rigid symmetric monoidal category
the set of isomorphism classes $\QCiso{G}$ forms a group.
Motivated by the sheaf-function dictionary for commutative, connected
algebraic groups \cite{SGA4.5}, we explore the trace of Frobenius morphism
\[
\QCiso{G} \to \Hom(G(\Fq), \EEx)
\]
and show that it is an isomorphism in Theorem \ref{thm:snake}, assuming only
that the geometric component group of $G$ is finitely generated.

We apply Theorem \ref{thm:snake} to the geometrization of quasicharacters
of non-Archimedian tori in Part 2.  Let $K$ be a non-Archimedian local field
with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
Write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$.
Let $T$ be a torus defined over $K$.  The N\'eron model $\TT$ of $T$
is a smooth group scheme over $\OK$ with generic fiber $T$ and a canonical isomorphism
$\TT(\OK) \cong T(K)$.  For each positive integer $d$, let $\GN{T}_d$ be the
Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^d}$; the commutative
group scheme $\GN{T}_d$ plays the r\^{o}le of $G$.  Theorem \ref{thm:application}
now provides a geometrization of quasicharacters of $T$ in the form of a canonical isomorphism
\[
\QCiso{\GN{T}_d} 
\iso
\Hom_{< d}(T(K),\EEx)
\] 
between quasicharacter sheaves on $\GN{T}_d$ and characters of $T(K)$ with depth less than $d$.
We also describe a group scheme $\GN{T}$ simultaneously geometrizing all quasicharacters of $T(K)$.

@@

We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
Analogous sheaves on connected, commutative algebraic groups were first studied
by Deligne \cite{SGA4.5}, and more recently Drinfeld has referred to such objects
as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem \ref{thm:snake}
is a direct generalization of the sheaf-function dictionary to the case of commutative
group schemes which are not necessarily connected or finite type.  The other main use
of the term ``character sheaf'' traces back to Lusztig \cite{}.  Most of his energy is devoted to
handling non-commutative groups; though he does define character sheaves for some
non-connected groups he restricts his attention to reductive groups with cyclic component group.
For extensions of $\ZZ/n\ZZ$ by a torus, it is not difficult to relate his Frobenius-stable character
sheaves to our quasicharacter sheaves.

We close the introduction with a more detailed description of the structure of this paper.
In Section \ref{sec:category} we define quasicharacter sheaves and give an interpretation of
them as Weil sheaves with a Galois action.
Section \ref{sec:Frob} introduces the trace of Frobenius homomorphism,
one direction of the sheaf-function dictionary.
We define pullbacks and products of quasicharacter sheaves in Section \ref{sec:pullback}, and use
them to prove a functoriality result on the trace of Frobenius.
In Section \ref{sec:basechange} we study how quasicharacter sheaves behave under base change
and Weil restriction.
Sections \ref{sec:bounded} and \ref{sec:finite} describe bounded and finite quasicharacter sheaves,
two subcategories of $\QC(G)$.  These alternate descriptions of quasicharacter sheaves play a key
role in the proof of Proposition \ref{prop:restriction}.
In section \ref{sec:connected} we show that bounded and finite quasicharacter sheaves are the same
as standard quasicharacter sheaves when $G$ is connected, and that trace of Frobenius is an isomorphism.
We shift to \'etale group schemes $G$ in Section \ref{sec:etale} and give a more concrete interpretation
of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
we give an isomorphism between $\QCiso{G}$ and $\Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))$.
Section \ref{sec:etalecohom} proves a result in Galois cohomology that shows that trace of Frobenius is
an isomorphism for \'etale group schemes.
In Section \ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
induces an essentially surjective functor of quasicharacter sheaves.
Section \ref{sec:snake} closes out Part \ref{part1} with the proof of the main theorem, that trace of Frobenius
is an isomorphism for $G$ as long as the geometric component group is finitely generated.

In Section \ref{sec:GAN} we introduce N\'eron models of tori and the Greenberg transform, which produce
group schemes over $\Fq$ from algebraic tori $T$ over $K$.
Section \ref{sec:bdchar} then uses Theorem \ref{thm:snake} to give a geometrization of characters of $T$
of bounded depth.
We give a reinterpretation of this result in Section \ref{sec:quasichar}, using a limit process to simultaneously
geometrize all quasicharacters of $T$.  Sections \ref{sec:bdchar} and \ref{sec:quasichar} also include
functoriality results that we hope to use in a future discussion of class field theory.
Finally, we close the paper in Section \ref{sec:transfer} by discussing a transfer principle, which allows
a geometric transfer of characters between characteristic $p$ tori to characteristic $0$ tori.

@@

\part{Smooth commutative group schemes lft over finite fields} \label{part1}

@@

@@

\section{Pull-back and products}\label{sec:pullback}

@@

In the opposite direction, let $\Nm_{k'/k} : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
\[
\Nm_{k'/k}^* : G(k)^* \to G(k')^* \qquad \text{defined by}\qquad \chi \mapsto \chi\circ \Nm_{k'/k}.
\]
We can also interpret this operation on characters in terms of quasicharacter sheaves, as follows.

@@

\section{Connected commutative algebraic groups} \label{sec:connected}

@@

  Let $(\cs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
  Recall the definition of the character $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
  Let $f : G\to G$ be the Lang isogeny.
  Recall that $\ker f = G(\Fq) = G^{\Frob{\Fq}}$; 
  in particular, the action of $\Gal(\bFq/\Fq)$ on $\ker f$ is trivial.
  Let $V = \EE$ and let $\psi : \ker f \to \Aut(V)$ be the representation given by 
  $\psi(g)(v) = \trFrob{\cs{L}}(g) v$ for $v\in V$. 
  Then $(f,\psi)$ is a finite quasicharacter sheaf.

@@

\section{Commutative \'etale group schemes} \label{sec:etale}

@@

  Starting from $\cs{L}$, we define a cocyle $\tau_{\cs{L}} \in Z^1(\Weil{\Fq},G(\bFq)^*)$ as follows.
  For $x \in G(\bFq)$, $\cs{L}$ determines an isomorphism $\phi_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
  of one-dimensional $\EE$-vector spaces; define $\tau_\cs{L}$ by
  \begin{equation}\label{t}
   \phi_{x}(s(\Frob{\Fq}(x))) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
  \end{equation}
  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\cs{L}(\Frob{\Fq})(x)$ is just $t_\cs{L}(x)$, so the restriction of
  $\tau_\cs{L}(\Frob{k})$ to $G(k)$ is just $t_\cs{L}$.
  In general, conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
  the scalar $\tau_\cs{L}(\Frob{k})(x)$ is non-zero.  Moreover, condition~\ref{cs.1} forces
  $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$
  for all $x,y \in G(\bFq)$.  Now define $\tau_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ recursively by
  \[
   \tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^{\Frob{\Fq}} \tau_\cs{L}(\Frob{\Fq}^{n-1}),
  \]
  where $\Frob{\Fq}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
  to pointwise multiplication of functions.

  Although we used a global section $s$ in the definition of
  $\tau_\cs{L}$, the class of $\tau_\cs{L}$ does not depend on this
  choice. To see why, let $s_1$ and $s_2$ be two global sections of
  $\cs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
  For each $x \in G(\bFq)$ there is a unique scalar
  $a(x) \in \EEx$ such that $s_2(x) = a(x) s_1(x)$. Then \eqref{section} and
  condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
  defined by $\tau_0(\Frob{\Fq}) = \,^{\Frob{\Fq}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
  so $\tau_2$ and $\tau_1$ are cohomologous. Thus
  \begin{equation}\label{cohomologous}
    \obj \QC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
    \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
  \end{equation}
  is independent of the choice of global sections made above.

@@

\section{On the cohomology of the dual of an etale group scheme} \label{sec:etalecohom}
%\input{etale-2}
%Define $\rho \colon \Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))
% \rightarrow \Hom(G(\Fq), \EEx)$ by $\rho(\phi)(g) =
% \phi(\Frob)(g)$.

@@

\begin{proposition}\label{prop:X}
  Let $X$ be a finitely generated abelian group equipped with an
  action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on
  $X$.  Then
  \begin{align*}
%    \Hh^1(\Fq, \Hom(X, \EEx)) &\xrightarrow{\rho} \Hom(\Hh^0(\Fq, X), \EEx) \\
    \Hh^1(\Fq, X^*) &\xrightarrow{\rho} \Hh^0(\Fq, X)^* \\
    \rho([z])(x) &= z(\Frob{\Fq})(x)
  \end{align*}
  is an isomorphism of groups.
\end{proposition}
\begin{proof}
  We first prove that $\rho$ is surjective.  Suppose that
  $f \in \Hom(X^{\Frob{\Fq}}, \EEx).$ Since $\EEx$ is divisible
  as an abelian group it is injective as a $\ZZ$-module and thus
  $\Ext^1_{\ZZ}(X/X^{\Frob{\Fq}}, \EEx) = 0$.  Applying the functor
  $\Hom(\mbox{---}, \EEx)$ to
  \[
  \begin{tikzcd}
  0 \rar & X^{\Frob{\Fq}} \rar & X \rar & X/X^{\Frob{\Fq}} \rar & 0
  \end{tikzcd}
  \]
  and considering the associated long exact sequence gives the
  existence of an $\tilde{f} \in \Hom(X, \EEx)$ restricting to
  $f$.  Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EEx))$ by
  mapping $\Frob{\Fq}$ to $\tilde{f}$.  Then $\rho([z]) = f$.

@@

\section{Restriction to the identity component} \label{sec:restriction}

@@

We have already seen that the trace of Frobenius defines a canonical homomorphism $\QCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
In this section we show that this homomorphism is functorial, in the following sense.

@@

\section{Application to quasicharacters of bounded depth} \label{sec:bdchar}

@@

\section{The geometrization of quasicharacters} \label{sec:quasichar}

@@

\section{The transfer principle} \label{sec:transfer}
